PM Mungbean meta-analysis

### 2019-06-19 02_Preliminary_analysis.Rmd
Cleaning up 02_Preliminary data Chunck data_summary

---
title: "PM Mungbean meta-analysis"
author: "P. Melloy"
date: "30 April 2019"
output: html_document
---

```{r include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
```

## Powdery Mildew analysis 2011 - 2017
### Summary of data

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(openxlsx)
source("Cleaning historical data.R", echo = FALSE, print.eval = FALSE)
# ___ Datasets available ___
# data   Herm_16.DR     - mean powdery mildew Disease rating data and mean Yield from two field trials in 2017, Hermitage and Fogerty
# data   King_16.DR     - mean powdery mildew Disease rating data and mean Yield from two field trials in 2016, Hermitage and Kingaroy
# data   Fogerty_17.1   - Full disease ratings and yeild data from Fogerty field trial in 2017
# data   Herm_17.1      - Full disease ratings and yeild data from Hermitage field trial in 2017
# data   PM_MB_17       - Full disease ratings and yeild data from Hermitage and Fogerty in 2017
# data   PM_MB_16       - End of season powdery mildew rating and Yield data from two field trials in 2016, Hermitage and Kingaroy
# data   PM_MB_means    - Mean disease rating and yeild data, from trial reports
PM.dat <- read.xlsx("C:/Users/U8011054/OneDrive - USQ/Cloudstor/Mungbean/1902 powdery mildew-Mungbean - Collated means.xlsx",
                    sheet = "Sheet1", startRow = 1, colNames = TRUE, detectDates = TRUE)
knitr::kable(
PM.dat %>%
   group_by(Trial_ref, Year, Location, trial_design, Replicates, planting_date, emergence_date, first_sign_disease) %>%
   summarise(Treatments = length(E_treatment))
)
PM.dat$Trial_ref <- factor(PM.dat$Trial_ref)
PM.dat$Location <- factor(PM.dat$Location)
PM.dat$Year <- factor(PM.dat$Year)
PM.dat$host_genotype <- factor(PM.dat$host_genotype)
PM.dat$Fungicide <- factor(PM.dat$Fungicide)
PM.dat$Trade_name <- factor(PM.dat$Trade_name)
#glimpse(PM.dat)
#str(PM.dat)
first1 <- PM.dat %>%
   group_by(Trial_ref, Location) %>%
   summarise(First_sign = mean(first_sign_disease, na.rm = T)) %>%
   filter(Location == "Kingaroy")

King_first <- subset(first1, Location == "Kingaroy")$First_sign
```

### Plotting weather data

@@

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Need weather data between 2011 and 2017
library(ggplot2)

>>>>

# Preliminary Analysis

```{r PA_Libraries, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(openxlsx)
library(kableExtra)
library(ggplot2)

## Summary of data

```{r data_summary, echo=TRUE, message=FALSE, warning=FALSE}

source("Cleaning historical data.R", echo = FALSE, print.eval = FALSE)
# ___ Datasets available ___
# data   Herm_16.DR     - mean powdery mildew Disease rating data and mean Yield from two field trials in 2017, Hermitage and Fogerty
# data   King_16.DR     - mean powdery mildew Disease rating data and mean Yield from two field trials in 2016, Hermitage and Kingaroy
# data   Fogerty_17.1   - Full disease ratings and yeild data from Fogerty field trial in 2017
# data   Herm_17.1      - Full disease ratings and yeild data from Hermitage field trial in 2017
# data   PM_MB_17       - Full disease ratings and yeild data from Hermitage and Fogerty in 2017
# data   PM_MB_16       - End of season powdery mildew rating and Yield data from two field trials in 2016, Hermitage and Kingaroy
# data   PM_MB_means    - Mean disease rating and yeild data, from trial reports

PM.dat <- read.csv("data/1902 powdery mildew-Mungbean - Collated means.csv")

glimpse(PM.dat)

kable(PM.dat %>%
   group_by(Trial_ref, Year, Location, trial_design, Replicates, planting_date, emergence_date, first_sign_disease) %>%
   summarise(Treatments = length(E_treatment)),
   caption = "Description of Experiments") %>%
   kable_styling(fixed_thead = T, full_width = T) %>%
   scroll_box(width = "900px", height = "500px")

PM.dat$Trial_ref <- factor(PM.dat$Trial_ref)
PM.dat$Location <- factor(PM.dat$Location)
PM.dat$Year <- factor(PM.dat$Year)
PM.dat$host_genotype <- factor(PM.dat$host_genotype)
PM.dat$Fungicide <- factor(PM.dat$Fungicide)
PM.dat$Trade_name <- factor(PM.dat$Trade_name)

## Weather data

@@

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Need weather data between 2011 and 2017
